|

### 2023-05-08 manuscript/Chapter2-appendix1.Rmd
notes on appendix 1
update appendix1

@@

# Extract the fixed effects from the model
eff_tab <- data.table(fixef(fit), keep.rownames = TRUE)
eff_tab <- eff_tab[, c(1, 2, 4:5)]

# Rename variables
setnames(
  eff_tab,
  c("rn", "Q2.5", "Q97.5"),
  c("parameter", "lower_ci", "upper_ci")
)

# Add a column that specifies the experience level
eff_tab[parameter %like% "novice", xp_level := "novice"]
eff_tab[parameter %like% "interm", xp_level := "intermediate"]
eff_tab[parameter %like% "advanced", xp_level := "advanced"]

# Back transform success
eff_tab[
  parameter %like% "success",
  c(2:4) := lapply(.SD, function(x) {plogis(x)}),
  .SDcols = c(2:4)
]

# Back transform sigma
eff_tab[
  parameter %like% "sigma",
  c(2:4) := lapply(.SD, function(x) {exp(x)}),
  .SDcols = c(2:4)
]

# Round values to 3 digits
eff_tab[, c(2:4) := round(eff_tab[, c(2:4)], digits = 2)]

# Reorganize the table ------------------------------------------------------

# reorder columns, and then rows based on xp level
eff_tab <- eff_tab[, c(5, 1:4)]
setorder(
  eff_tab,
  cols = -"xp_level"
)

# Create trait column
eff_tab[
  , trait := rep(c(
    "predator speed", "predator speed",
    "prey speed", "prey speed", "hunting success"),
    6
  )
]

# Rename parameter
eff_tab[
   , parameter := rep(
      c(
         rep(c("intercept (mean)", "intercept (sigma)"), 2),
         "intercept (mean)",
         rep(c("prey rank (mean)", "prey rank (sigma)"), 2),
         "match duration (mean)"
      ),
      3
   )
]

# Paste upper and lower ci with estimate
eff_tab[, estimate := paste(format(Estimate, digits = 2), "(")]
eff_tab[, estimate := paste(estimate, format(lower_ci, digits = 2), sep = "")]
eff_tab[, estimate := paste(estimate, ",", sep = "")]
eff_tab[, estimate := paste(estimate, format(upper_ci, digits = 2), sep = " ")]
eff_tab[, estimate := paste(estimate, ")", sep = "")]
eff_tab[, c("Estimate", "lower_ci", "upper_ci") := NULL]

# Reshape
eff_tab <- dcast(
  eff_tab,
  trait + parameter ~ xp_level,
  value.var = "estimate"
)

# Reorder columns
eff_tab <- eff_tab[, c(1, 2, 5, 4, 3)]

# Reorder rows
table <- eff_tab[c(3, 5, 4, 6, 7, 9, 8, 10, 1, 2)]

@@

  # Table caption
  set_caption(
    caption = "Table S1. Posterior means and 95% credible intervals of the fixed effects estimated by the MDHGLM of predator speed, prey speed, and predator hunting success.",
    style = "Table Caption"
  ) %>%

@@

# Summarize values
ranef_tab[, ":=" (mean = mean(value),
                  lower_ci = lower_interval(value),
                  upper_ci = upper_interval(value)),
          by = .(parameter)]

ranef_tab <- unique(ranef_tab[, .(parameter, mean, lower_ci, upper_ci)])
ranef_tab[, c(2:4) := round(ranef_tab[, c(2:4)], digits = 2)]

@@

# Paste upper and lower ci with estimate
ranef_tab[, estimate := paste(format(mean, digits = 2), "(")]
ranef_tab[, estimate := paste(estimate, format(lower_ci, digits = 2), sep = "")]
ranef_tab[, estimate := paste(estimate, ",", sep = "")]
ranef_tab[, estimate := paste(estimate, format(upper_ci, digits = 2), sep = " ")]
ranef_tab[, estimate := paste(estimate, ")", sep = "")]
ranef_tab[, c("mean", "lower_ci", "upper_ci") := NULL]

@@

  # Add footnote
  footnote(
    i = 1, j = 1,
    part = "header",
    value = as_paragraph(
      as_sup("a "),
      "We exponentiated the dispersion parameters (i.e. sigma) which are estimated on a log scale. All the reported values are standard deviations.",
      as_sup("\nb "),
      "The intercept values on the mean part of the equation for all traits indicate among individual differences in mean behaviour and success.",
      as_sup("\nc "),
      "The intercept values on the dispersion (i.e. sigma) part of the equation for predator speed indicate among individual differences in behavioural specialization. For prey speed and hunting success, they indicate among individual differences in the variability of prey encounters and variability in hunting success, respectively."
    ),
    ref_symbols = " "
  ) %>%

  # Add table caption
  set_caption(
    caption = "Table S2. Posterior means and 95% credible intervals of the random effects estimated by the MDHGLM of predator speed, prey speed, and predator hunting success.",
    style = "Table Caption"
  ) %>%

>>>>

Update the plot legend to tell what is the *greatest increase*

@@

# Extract the fixed effects posterior samples
b_draws <- data.table(
  as_draws_df(
    fit, variable = "^b_", regex = TRUE
  )
)

b_draws[, c(31:33) := NULL]

# Back-transform the parameters ----------------------------------------------

# Take the exponent of sigma parameters
b_draws[
  , c("b_sigma_speednovice_Intercept",
      "b_sigma_speedinterm_Intercept",
      "b_sigma_speedadvanced_Intercept",
      "b_sigma_preyspeednovice_Intercept",
      "b_sigma_preyspeedinterm_Intercept",
      "b_sigma_preyspeedadvanced_Intercept",
      "b_sigma_speednovice_sqrt_prey_avg_rank",
      "b_sigma_speedinterm_sqrt_prey_avg_rank",
      "b_sigma_speedadvanced_sqrt_prey_avg_rank",
      "b_sigma_preyspeednovice_sqrt_prey_avg_rank",
      "b_sigma_preyspeedinterm_sqrt_prey_avg_rank",
      "b_sigma_preyspeedadvanced_sqrt_prey_avg_rank"
  )
  := lapply(.SD, function(x) {exp(x)}),
  .SDcols = c(
    "b_sigma_speednovice_Intercept",
    "b_sigma_speedinterm_Intercept",
    "b_sigma_speedadvanced_Intercept",
    "b_sigma_preyspeednovice_Intercept",
    "b_sigma_preyspeedinterm_Intercept",
    "b_sigma_preyspeedadvanced_Intercept",
    "b_sigma_speednovice_sqrt_prey_avg_rank",
    "b_sigma_speedinterm_sqrt_prey_avg_rank",
    "b_sigma_speedadvanced_sqrt_prey_avg_rank",
    "b_sigma_preyspeednovice_sqrt_prey_avg_rank",
    "b_sigma_preyspeedinterm_sqrt_prey_avg_rank",
    "b_sigma_preyspeedadvanced_sqrt_prey_avg_rank"
  )
]

# plogis for the success parameters
# Take the exponent of sigma parameters
b_draws[
  , c("b_successnovice_Intercept",
      "b_successinterm_Intercept",
      "b_successadvanced_Intercept",
      "b_successnovice_sqrt_game_duration",
      "b_successinterm_sqrt_game_duration",
      "b_successadvanced_sqrt_game_duration"
  )
  := lapply(.SD, function(x) {plogis(x)}),
  .SDcols = c(
    "b_successnovice_Intercept",
    "b_successinterm_Intercept",
    "b_successadvanced_Intercept",
    "b_successnovice_sqrt_game_duration",
    "b_successinterm_sqrt_game_duration",
    "b_successadvanced_sqrt_game_duration"
  )
]

fixef_tab <- melt(
  b_draws,
  variable.name = "parameter"
)

# Summarize the values (medians + 95% CI) -------------------------------------

# Summarize values
fixef_tab[, ":=" (median = median(value),
                  lower_ci = lower_interval(value),
                  upper_ci = upper_interval(value)),
          by = .(parameter)]

fixef_tab <- unique(fixef_tab[, .(parameter, median, lower_ci, upper_ci)])
fixef_tab[, c(2:4) := round(fixef_tab[, c(2:4)], digits = 2)]

# Add a column that specifies the experience level
fixef_tab[parameter %like% "novice", xp_level := "novice"]
fixef_tab[parameter %like% "interm", xp_level := "intermediate"]
fixef_tab[parameter %like% "advanced", xp_level := "advanced"]

# Paste upper and lower ci with estimate
fixef_tab[, estimate := paste(format(median, digits = 2), "(")]
fixef_tab[, estimate := paste(estimate, format(lower_ci, digits = 2), sep = "")]
fixef_tab[, estimate := paste(estimate, ",", sep = "")]
fixef_tab[, estimate := paste(estimate, format(upper_ci, digits = 2), sep = " ")]
fixef_tab[, estimate := paste(estimate, ")", sep = "")]
fixef_tab[, c("median", "lower_ci", "upper_ci") := NULL]

# reorder columns, and then rows based on xp level
setorder(
  fixef_tab,
  cols = -"xp_level"
)

# Create trait column
fixef_tab[
  , trait := rep(c(
    "predator speed", "predator speed",
    "prey speed", "prey speed", "hunting success"),
    6
  )
]

# Rename parameter column
fixef_tab[
  , parameter := rep(
    c(
      rep(c("intercept (mean)", "intercept (sigma)"), 2),
      "intercept (mean)",
      rep(c("prey rank (mean)", "prey rank (sigma)"), 2),
      "match duration (mean)"
    ),
    3
  )
]

# Reshape
fixef_tab <- dcast(
  fixef_tab,
  trait + parameter ~ xp_level,
  value.var = "estimate"
)

# Reorder columns and rows
fixef_tab <- fixef_tab[, c(1, 2, 5, 4, 3)]
table <- fixef_tab[c(3, 5, 4, 6, 7, 9, 8, 10, 1, 2)]

@@

  # Table caption
  set_caption(
    caption = "Table S1. Posterior medians and 95% credible intervals of the fixed effects estimated by the MDHGLM of predator speed, prey speed, and predator hunting success.",
    style = "Table Caption"
  ) %>%

@@

# Summarize values
ranef_tab[, ":=" (median = median(value),
                  lower_ci = lower_interval(value),
                  upper_ci = upper_interval(value)),
          by = .(parameter)]

ranef_tab <- unique(ranef_tab[, .(parameter, median, lower_ci, upper_ci)])
ranef_tab[, c(2:4) := round(ranef_tab[, c(2:4)], digits = 2)]

@@

# Paste upper and lower ci with estimate
ranef_tab[, estimate := paste(format(median, digits = 2), "(")]
ranef_tab[, estimate := paste(estimate, format(lower_ci, digits = 2), sep = "")]
ranef_tab[, estimate := paste(estimate, ",", sep = "")]
ranef_tab[, estimate := paste(estimate, format(upper_ci, digits = 2), sep = " ")]
ranef_tab[, estimate := paste(estimate, ")", sep = "")]
ranef_tab[, c("median", "lower_ci", "upper_ci") := NULL]

@@

  # Add footnote
  footnote(
    i = 1, j = 1,
    part = "header",
    value = as_paragraph(
      as_sup("a "),
      "We exponentiated the dispersion parameters (i.e. sigma) which are estimated on a log scale. All the reported values are standard deviations.",
      as_sup("\nb "),
      "The standard deviation values on the mean part of the equation indicate, for all traits, among individual differences in mean behaviour, prey encountered, and success.",
      as_sup("\nc "),
      "Values on the dispersion (i.e. sigma) for predator speed indicate among individual differences in behavioural specialization. For prey speed, they indicate among individual differences in the variability of prey encounters."
    ),
    ref_symbols = " "
  ) %>%

  # Add table caption
  set_caption(
    caption = "Table S2. Posterior medians and 95% credible intervals of the random effects estimated by the MDHGLM of predator speed, prey speed, and predator hunting success. All the reported values are standard deviations.",
    style = "Table Caption"
  ) %>%
